Metric Spaces with Expensive Distances

### 2019-12-04 paper/draft_socg.tex
Minor changes in paper

Alternatively, one could also compute the Earth Mover's distance
on gray value images by considering each image as a distribution on pixels.
The results of this experiment are in \cref{sec:spanners_euclidean_addendum}, since this variant
does not seem to be used in applications.

@@

We randomly selected 250 images from the dataset.
The results of the experiment are summarized in \cref{tbl:emd_gtsrb}.
As in \cref{sec:experiment_spanners}, 
the first two columns give the sparseness.
For smaller values of $\eps$,
the \bgrdy spanner contains approximately 3 times more
edges than the greedy spanner, so the ratio is roughly
the same as for persistence diagrams.
The last 3 columns compare the running time.
Note that even for $\eps=0.1$,
the \bgrdy spanner saves $70\%$ of the computation time.
If we allow large relative error,
we see the speed by almost a factor of $10$.

>>>>

Alternatively, we also experimented with the Earth Mover’s distance on
gray value images by considering each image as a distribution on pixels.
For this (non-standard) variant, we obtain even larger speed-ups~-- see
\cref{sec:spanners_euclidean_addendum} for details.

@@

We randomly selected 250 images from the dataset.
The results of the experiment are summarized in \cref{tbl:emd_gtsrb}.
As in \cref{sec:experiment_spanners}, 
the first two columns give the sparseness.
For smaller values of $\eps$,
the \bgrdy spanner contains approximately 3 times more
edges than the greedy spanner, so the ratio is roughly
the same as for persistence diagrams.
The last 3 columns compare the running time.
Note that even for $\eps=0.1$,
the \bgrdy spanner saves $70\%$ of the computation time.
If we allow large relative error,
we see the speed up by almost a factor of $10$.
